---
title: "Comparing MCMC Runs Test Tasks"
author: "Thiloshon Nagarajah"
date: "March 3, 2018"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a demonstration of test tasks given in the Comparing MCMC runs project at <https://github.com/rstats-gsoc/gsoc2018/wiki/Comparing-MCMC-runs#solutions-of-tests>.

The source code can be accessed at <https://github.com/thiloshon/GSoC-2018-MCMC>.

## Object Creation
First, let's create a sampleInfoClass object.

```{r echo=F, eval=T}
set.seed(1000)
sampleInfoClass <-
    setRefClass("sampleInfoClass",
        fields = list(vector = "numeric", vectorMetrics = "list"),
        methods = list(
            initialize = function(vector = NA, vectorMetrics = list()) {
                .self$vector <- vector
                .self$vectorMetrics <- vectorMetrics
                .self$message()
            },
            message = function() {
                cat("New sampleInfoClass instance created.")
            }
        )
    )

sampleInfoCollectionClass <-
    setRefClass("sampleInfoCollectionClass",
        fields = list(sampleInfoClasses = "list"),
        methods = list(
            initialize = function(sampleInfoClasses = NA) {
                "Construct an instance of sampleInfoCollectionClass after validating the type."
                
                if (class(sampleInfoClasses[[1]]) != "sampleInfoClass") {
                    stop("Incompatible input type. Provide a list of sampleInfoClass")
                }
                .self$sampleInfoClasses <- sampleInfoClasses
                .self$message()
            },
            
            message = function() {
                cat("New sampleInfoCollectionClass instance created.")
            }
        )
    )


sampleInfoCollectionClass$methods(
    calculateScalar = function(FUN = mean, ...) {
        "Computes a scalar metric from a numeric vectorm and assigns to the object"
        
        nameOfFun <- as.character(substitute(FUN))
        
        lapply(sampleInfoClasses, function(x) {
            x$vectorMetrics[[nameOfFun]] <- FUN(x$vector)
        })
    }
)

sampleInfoCollectionClass$methods(
    generatePlot = function(metric = "mean", plotFun = barplot, ...) {
        "Creates a barplot by extracting the named metric from each object"
        
        if (is.null(sampleInfoClasses[[1]]$vectorMetrics[[metric]])) {
            stop(paste(metric, "not calculated yet!"))
        }
        
        df <- data.frame(unlist(
            lapply(sampleInfoClasses, function(x) {
                x$vectorMetrics[[metric]]
            })
        ))
        
        plotFun(df[, 1], ...)
    }
)

sampleInfoCollectionClass$methods(
    plotToHTML = function(file = "index.html"){
        "Generates an html page from the plot created in generatePlot() function"
        
        require(R2HTML)
        HTMLplot(file = file, append = F)
        cat(paste("Plot is saved to ", getwd()))
    }   
)
```


```{r echo=T, eval=T}
infoClassObj1 <- sampleInfoClass(vector = sample(5))
infoClassObj2 <- sampleInfoClass(vector = sample(20))
```

Now, let's check what the objects contain.

```{r echo=T, eval=T}
infoClassObj1
infoClassObj2
```

Now, let's create a sampleInfoCollectionClass object and check the content.

```{r echo=T, eval=T}
infoCollection <- sampleInfoCollectionClass(sampleInfoClasses = list(infoClassObj1, infoClassObj2))
infoCollection
```

Great! The two sampleInfoClasses are in the object. 

## Methods and Object Manipulation

Now let's try to calculate the mean of the objects in infoCollection.

```{r echo=T, eval=T}
infoCollection$calculateScalar(FUN = mean)
```

And calculate the max as well.

```{r echo=T, eval=T}
infoCollection$calculateScalar(FUN = max)
infoCollection
```

As you can see, two new list elements are present in the vectorMetrics, namely, `$mean` and `$max`.


## Plotting and Object Visualization

Now, at last, let's create a simple plot for the average of the objects.

```{r echo=T, eval=T}
infoCollection$generatePlot(metric = "mean")
```

And a plot with custom plot settings.

```{r echo=T, eval=T}
infoCollection$generatePlot(
    metric = "mean",
    barplot,
    main = "sampleInfoClass Scalar Plot",
    xlab = "Average",
    col = "blue"
    )
```









